---
title: "ThReshold selection."
author: "Knecmab"
date: "Tuesday, November 18, 2014"
output: html_document
---

ThReshold selection for bi-modal data.
================================================================================

First lets load the package and get a data set.

```{r, message=FALSE}
require(threshold)
ds <- twoGaussians(seed=123)
hist(ds$x, breaks='Scott', freq=FALSE)
```

And see what the different threshold selection methods do.

`rosin` threshold:

```{r, warning=FALSE, message=FALSE}
th_rosin <- find_threshold(ds$x, method="rosin")
th_rosin
plot.threshold(th_rosin)
```

`valleys` threshold:

```{r, warning=FALSE, message=FALSE}
th_valleys <- find_threshold(ds$x, method="valleys")
th_valleys
plot(th_valleys)
```


`nmm` threshold:

```{r, warning=FALSE, message=FALSE}
th_nmm <- find_threshold(ds$x, method="nmm")
th_nmm
plot(th_nmm)
```


`entropy` threshold:

```{r, warning=FALSE, message=FALSE}
th_entropy <- find_threshold(ds$x, method="entropy")
th_entropy
plot(th_entropy)
```


ThReshold selection for tri-modal data.
================================================================================

First lets load the package and get a data set.

```{r, message=FALSE}
require(threshold)
ds <- threeGaussians(seed=123)
hist(ds$x, breaks='Scott', freq=FALSE)
```

And see what the different threshold selection methods do.

`rosin` threshold:

```{r, warning=FALSE, message=FALSE}
th_rosin <- find_threshold(ds$x, method="rosin")
th_rosin
plot.threshold(th_rosin)
```

`valleys` threshold:

```{r, warning=FALSE, message=FALSE}
th_valleys <- find_threshold(ds$x, method="valleys")
th_valleys
plot(th_valleys)
```


`nmm` threshold:

```{r, warning=FALSE, message=FALSE}
th_nmm.g2 <- find_threshold(ds$x, method="nmm", G=2)
th_nmm.g2

th_nmm.g9 <- find_threshold(ds$x, method="nmm", G=9)
th_nmm.g9

par(mfrow=c(1,2))
plot(th_nmm.g2)
plot(th_nmm.g9)
```


`entropy` threshold:

```{r, warning=FALSE, message=FALSE}
th_entropy <- find_threshold(ds$x, method="entropy")
th_entropy
plot(th_entropy)
```


ThReshold selection for uni-modal data.
================================================================================

First lets load the package and get a data set.

```{r, message=FALSE}
require(threshold)
ds <- twoGaussians(seed=123, m.pos=0)
hist(ds$x, breaks='Scott', freq=FALSE)
```

And see what the different threshold selection methods do.

`rosin` threshold:

```{r, warning=FALSE, message=FALSE}
th_rosin <- find_threshold(ds$x, method="rosin")
th_rosin
plot.threshold(th_rosin)
```

`valleys` threshold:

```{r, warning=FALSE, message=FALSE}
th_valleys <- find_threshold(ds$x, method="valleys")
th_valleys
plot(th_valleys)
```


`nmm` threshold:

```{r, warning=FALSE, message=FALSE}
th_nmm <- find_threshold(ds$x, method="nmm")
th_nmm
plot(th_nmm)
```


`entropy` threshold:

```{r, warning=FALSE, message=FALSE}
th_entropy <- find_threshold(ds$x, method="entropy")
th_entropy
plot(th_entropy)
```

ThReshold selection - run all at once.
================================================================================

```{rU}
ths <- find_threshold(ds$x, method=c("rosin", "entropy", "valleys", "nmm"))
ths
plot(ths)
plot(ths)


# You might also want to compare it to another set of thresholds.
plot(ths, ths_add=list('my_th_1'=c(1),
                       'my_th_2'=c(4, 4.2)))


```


