---
title: "ThReshold selection for one-class classifiers."
author: "Knecmab"
date: "Tuesday, November 18, 2014"
output: html_document
---

One-class classification
========================

Threshold selection is a critical step during one-class classification. 
The package `thReshold` provides methods for this task. 

The one-class classifiction problem can be solved with positive data only (LEFT plot), positive and unlabeled data (MIDDLE plot). It is different from a binary supervised classifier with respect to the training data (RIGHT plot.) 

```{r, echo=FALSE, fig.height=3, message=FALSE}
require(oneClass)
data(bananas)
x.pu <- bananas$tr[, -1]
y.pu <- bananas$tr[, 1]

idx.p <- y.pu==1
x.p <- x.pu[idx.p, ]
y.p <- y.pu[idx.p]

set.seed(6)
idx.n <- sample(which(bananas$y[]==-1), nrow(x.p))
x.pn <- rbind(x.p, bananas$x[][idx.n,])
y.pn <- rep(c(1,0), each=nrow(x.p))

par(mfrow=c(1,3))
plot(x.p$x1, x.p$x2, pch=16, xlab="x1", ylab="x2")
plot(x.pu$x1, x.pu$x2, pch=c(4, 16)[y.pu+1],
     xlab="x1", ylab="x2")
plot(x.pn$x1, x.pn$x2, pch=c(1, 16)[y.pu+1],
     xlab="x1", ylab="x2")
```

Using a one-class SVM we might find a model as shown in the next plot below. 
(Note that in the case of the one-class SVM only the positive data can be used for model training but in the `oneClass` package the unlabeled data is used for model selection.)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
require(oneClass)
fit <- trainOcc(x=x.pu, y=y.pu, method='ocsvm')
pred <- predict(fit, bananas$x[])
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5, fig.width=5, results='asis', out.extra=''}
featurespace(fit, threshold=0)
```

Applying this model to the whole unlabeled data to be classified leads to the histogram of predictive values shown in the next plot. 
The distributions of the hold-out training data predictions is shown as boxplots below the histogram. 

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.width=5, results='asis', out.extra=''}
hist(fit, pred)
abline(v=0, lwd=2)
```

ThReshold selection
========================

